
---
title: "allcontributor"
output:
  rmarkdown::html_vignette:
    self_contained: no

  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE,
  message = TRUE,
  width = 120,
  comment = "#>",
  fig.retina = 2,
  fig.path = "README-"
)
```

<!-- badges: start -->

[![R build
status](https://github.com/mpadge/allcontributor/workflows/R-CMD-check/badge.svg)](https://github.com/mpadge/allcontributor/actions?query=workflow%3AR-CMD-check)
[![Project Status:
Concept](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

Acknowledge all contributors in your 'README'. Just an alternative
implementation in R of the original
[`all-contributors`](https://github.com/all-contributors/all-contributors), but
at the moment restricted to automatic addition of direct code contributors
only.

## Installation

Currently only on github, so package must be installed with

```{r install, eval = FALSE}
remotes::install_github("mpadge/allcontributor")
```

The package can then be loaded the usual way:
```{r load, echo = FALSE, message = FALSE}
devtools::load_all (".", export_all = FALSE)
```
```{r load-fakey, eval = FALSE}
library (allcontributor)
```


## Usage

The package has only two functions, `get_contributors()`, to return a list of
repository contributors, and the primary function, `add_contributors()`, which
renders the results of this function in a table in the `README.Rmd` and
`README.md` files.


## Contributors

<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

This project follows the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

<table>

<tr>
<td align="center">
<a href="https://github.com/mpadge">
<img src="https://avatars1.githubusercontent.com/u/6697851?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/mpadge/allcontributor/commits?author=mpadge">mpadge</a>
</td>
</tr>

</table>

<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->

