
---
title: "allcontributors"
output:
  rmarkdown::html_vignette:
    self_contained: no

  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE,
  message = TRUE,
  width = 120,
  comment = "#>",
  fig.retina = 2,
  fig.path = "README-"
)
```

<!-- badges: start -->

[![R build
status](https://github.com/ropenscilabs/allcontributors/workflows/R-CMD-check/badge.svg)](https://github.com/ropenscilabs/allcontributors/actions?query=workflow%3AR-CMD-check)
[![codecov](https://codecov.io/gh/ropenscilabs/allcontributors/branch/master/graph/badge.svg)](https://codecov.io/gh/ropenscilabs/allcontributors)
[![Project Status:
Concept](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

An alternative implementation in R of the original
[`all-contributors`](https://allcontributors.org/) to acknowledge all
contributors in your 'README' (or elsewhere). The original is intended to help
acknowledge *all* contributions including those beyond the contents of an
actual repository (such as community or other or less-tangible organisational
contributions). This version restricts acknowledgements to direct and tangible
contributions to a repository only, but automates that task to a single
function call, in the hope that such simplicity will spur greater usage.
In short: This package can't do everything the original does, but it makes what
it does much easier.

## Why then?

The original [`all-contributors`](https://allcontributors.org/) is primarily
a bot which responds to commit messages such as `add @user for <contribution>`,
where `<contribution>` is one of the [recognized
types](https://allcontributors.org/docs/en/emoji-key). As said above, the
relative advantage of that original system lies primarily in the diversity of
contribution types able to be acknowledged, with each type for a given user
appearing as a corresponding
[emoji](https://allcontributors.org/docs/en/emoji-key) below their github
avatar as listed on the README. In comparison, this R package:

1. Works automatically, by calling `add_contributors()` at any time to add or
   update contributor acknowledgements.
2. Works locally without any bot integration
3. Can add contributors to any file, not just the main README
4. Offers a variety of formats for listing contributors:
   (i) divided into sections by types of contributions, or as a single section
   (ii) presented as full grids (like [the
        original](https://github.com/all-contributors/all-contributors/blob/master/README.md#contributors-)),
        numbered lists of github user names only, or single text strings of
        comma-separated names.

## Installation

Not yet on CRAN, so must be installed from remote repository host systems using
any one of the following options:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_git("https://git.sr.ht/~ropenscilabs/allcontributors")
remotes::install_bitbucket("mpadge/allcontributors")
remotes::install_gitlab("mpadge/allcontributors")
remotes::install_github("mpadge/allcontributors")
```

The package can then be loaded the usual way:
```{r load, echo = FALSE, message = FALSE}
devtools::load_all (".", export_all = FALSE)
```
```{r load-fakey, eval = FALSE}
library (allcontributors)
```

## Usage

The primary function of the package,
[`add_contributors()`](https://ropenscilabs.github.io/allcontributors/reference/add_contributors.html),
adds a table of all contributors by default to the main `README.md` file (and
`README.Rmd` if that exists). Tables or lists can be added to other files by
specifying the `files` argument of that function. The appearance of the
contributors table is determined by several parameters in that function,
including:

1. `type` For the type of contributions to include (code, contributors who open
   issues, contributors who discuss issues).
2. `num_sections` For whether to present contributors in 1, 2, or 3 distinct
   sections, dependent upon which `type`s of contributions are to be
   acknowledged.
3. `format` Determining whether contributors are presented in a grid with
   associated avatars of each contributor, as in [the
   original](https://github.com/all-contributors/all-contributors/blob/master/README.md#contributors-), 
   an enumerated list of github user names only, or a single text string of
   comma-separated names.

Contribution data are obtained by querying the github API, for which a local
key should be set as an environmental variable containing the name `"GITHUB"`
(either via `Sys.setenv()`, or as an equivalent entry in a file `~/.Renviron`).

If the main `README` file(s) contains a markdown section entitled
`"Contributors"`, the
[`add_contributors()`](https://ropenscilabs.github.io/allcontributors/reference/add_contributors.html)
function will add a table of contributors there, otherwise it will be appended
to the end of the document(s). If you wish your contributors table to be
somewhere other than at the end of the `README` file(s), start by adding an
empty `"## Contributors` section to the file(s) and the function will insert
the table at that point.

Any time you wish to update your contributor list, simply re-run the
`add_contributors()` function. There's even an `open_issue` parameter that will
automatically open or update a github issue on your repository so that
contributors will be pinged about them being added to your list of
contributors.

The data used to construct the contributions table can also be extracted
without writing to the `README` file(s) with the function
[`get_contributors()`](https://ropenscilabs.github.io/allcontributors/reference/get_contributors.html):

```{r get_contributors}
get_contributors(org = "ropenscilabs", repo = "allcontributors")
```


## Contributors


<!-- ALL-CONTRIBUTORS-LIST:START - Do not remove or modify this section -->
<!-- prettier-ignore-start -->
<!-- markdownlint-disable -->

This project uses the [`allcontributors` package](https://github.com/ropenscilabs/allcontributors) following the [all-contributors](https://allcontributors.org) specification. Contributions of any kind are welcome!

### Code

<table>

<tr>
<td align="center">
<a href="https://github.com/mpadge">
<img src="https://avatars1.githubusercontent.com/u/6697851?v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/ropenscilabs/allcontributors/commits?author=mpadge">mpadge</a>
</td>
</tr>

</table>


### Issue Authors

<table>

<tr>
<td align="center">
<a href="https://github.com/maelle">
<img src="https://avatars1.githubusercontent.com/u/8360597?u=144e03ae2bbe8a69318cb0c6c3f647e25aec6763&v=4" width="100px;" alt=""/>
</a><br>
<a href="https://github.com/ropenscilabs/allcontributors/issues?q=is%3Aissue+author%3Amaelle">maelle</a>
</td>
</tr>

</table>

<!-- markdownlint-enable -->
<!-- prettier-ignore-end -->
<!-- ALL-CONTRIBUTORS-LIST:END -->
